Review: Crop adaptation through introgression from wild relatives

### 2017-04-08 paper.tex
Update paper.tex

Whereas the process of domestication used to be concieved of as rapid and geographically-constrained, archaeological and genetic evidence has recently revealed that domestication is more often temporally-protracted and multiregional \cite{brown2009complex}.
This new paradigm emphasizes the role of gene flow of beneficial alleles into domesticating populations from sympatric, locally-adapted wild relatives, a process known as adaptive introgression.
Adaptive introgression has two steps: hybridization between two genomes (in the case of this review, a domesticated crop and its wild relative), followed by recombination and selection for progressively smaller genomic segments that harbor the adaptive locus/loci with fewer maladaptive alleles being dragged along \cite{Feuillet200824}.

>>>>

Whereas the process of domestication used to be concieved of as rapid and geographically-constrained, archaeological and genetic evidence has recently revealed that domestication is more often temporally-protracted and multiregional \cite{brown2009complex}.
This new paradigm emphasizes the role of gene flow of beneficial alleles into domesticating populations from sympatric, locally-adapted wild relatives, a process known as adaptive introgression.
Adaptive introgression has three components: hybridization between two genomes (in the case of this review, a domesticated crop and its wild relative), backcrossing to one of the parents (in this case, the domesticate), recombination, and selection on different recombinant genotypes with progressively smaller linkage \cite{barton2001role}.

followed by recombination and selection for progressively smaller genomic segments that harbor the adaptive locus/loci with fewer maladaptive alleles being dragged along \cite{Feuillet200824}.
Much attention has been given to the risk of natural introgression of transgenes from domessticated crops into wild relatives (for a review, \cite{stewart2003transgene}), or the history, utility, and methods of breeding programs designed to introgress desired traits from wild relatives (for a review, \cite{zamir2001improving, tanksley1997seed, hajjar2007use})
, but what
